\documentclass[11pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{ebgaramond}
\usepackage{titlesec}
\usepackage{enumitem}
\titleformat{\section} {\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]
\newcommand{\centertitle}[3]{
	{\noindent\bfseries
	\parbox[][0.5em][b]{0.35\textwidth}{#1\hfill}%
	\parbox[][0.5em][b]{0.3\textwidth}{\centerline{#2}}%
	\parbox[][0.5em][b]{0.35\textwidth}{\hfill#3}}
}

\pagestyle{empty}
\begin{document}

\noindent
\parbox{0.2\textwidth}{\,}
\parbox{0.6\textwidth}{\centerline{\huge\scshape\bfseries Wenqi He}}
\parbox{0.2\textwidth}{+1 (470) 343 - 5207 \\hewenqi96@gmail.com}

\section*{EDUCATION}
\centertitle{Atlanta, GA, USA}{Georgia Institute of Technology}{Aug. 2015 - Dec. 2019}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item \textbf{Bachelor of Science in Computer Science} \hfill major GPA: 4.0/4.0, cumulative GPA: 3.97/4.0
\item \textbf{Minor in Physics} (Graduate-level Coursework: General Relativity) \hfill \texttt{//galmungral.github.io/physics}
\item \textbf{CS Coursework:} OOP, Algorithms \& Data Structures, Analysis of Algorithms, Computer Organization, Operating Systems, Computer Networking, Relational Database, Information Security, Computer Simulation, Machine Learning (Incomplete)
\end{itemize}
\vspace{-0.5em}

\section*{EXPERIENCE}
\centertitle{Front-end Developer, Intern}{Pegasus CRM, Decatur, GA}{Jan. 2018 - May. 2018}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Provided a proof-of-concept \underline{\smash{Vue.js}} reimplementation of existing UI features for the team to evaluate framework adoptation.
\item Implemented designer's page designs using \underline{\smash{Blade PHP templates}} and \underline{SASS} in a \underline{Laravel} application.
\item Integrated resizing and drag-and-drop features to existing data tables using \underline{\smash{vanilla JavaScript}}.
\item Expedited bug fixing process by tracing into back-end code and identifying reported bugs that originate in the backend.
\end{itemize}
\vspace{-0.5em}

\section*{SOFTWARE PROJECTS \hfill \normalsize\texttt{//github.com/GalMunGral}}

\textbf{SitBit} \enspace \textit{Accelerometer-based sitting time recorder. (Proof of Concept) } 
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Utilized \underline{Core Motion} framework on iOS (\underline{Swift}) and the \underline{Sensor} framework on Android (\underline{Kotlin}) to detect acceleration.
\item Created a GitHub-style calendar heat map based on (mock) data pulled from backend using \underline{\smash{D3.js}} and \underline{SVG}.
\item Embedded the visualization in mobile app using \underline{WebView} on Android and \underline{WKWebView} on iOS. 
\item Implemented the back end in \underline{\smash{Golang}} with a \underline{\smash{MySQL}} database.
\end{itemize}
\vspace{0.5em}
%
\textbf{ReSpotify} \enspace \textit{Reimplementation of Spotify music player}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item  Recreated Spotify's playback/volume controls by integrating \underline{\smash{Spotify Web Playback SDK}} with a \underline{\smash{React.js}} UI.
\item Implemented \underline{OAuth 2.0} authorization flows in \underline{\smash{Python}} using \underline{\smash{Flask}} framework to access \underline{\smash{Spotify Web API}}.
\end{itemize}
\vspace{0.5em}
%
\textbf{NoTube} \enspace \textit{Reimplementation of YouTube Website (Proof of Concept)}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Partially replicated the UI using \underline{\smash{Angular.js}} and \underline{\smash{SASS}}. Implemented video streaming using \underline{\smash{Shaka player}} and \underline{\smash{FFmpeg}}.
\end{itemize}
\vspace{0.5em}
%
\textbf{WebREPL}  \enspace \textit{Interactive shell in browser, as commonly seen on coding websites such as Codeacademy}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Designed a mechanism to evaluate submitted scripts on server and send back output/error to be displayed in browser.
\item Implemented using a parent \underline{\smash{Node.js}} process that communicates with a \underline{\smash{Python}} interpreter child process.
\end{itemize}
\vspace{0.5em}
%
\textbf{TwoFactor} \enspace \textit{Two-factor authentication with push notifications (Proof of Concept)}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Implemented two-factor login using a \underline{\smash{Node.js}} backend that communicates with the login page through \underline{\smash{Socket.io}}.
\item Crafted push notification requests to \underline{\smash{Firebase Cloud Messaging}} and to \underline{\smash{Apple Push Notification Service}} in \underline{HTTP/2}.
\end{itemize}
\vspace{0.5em}
%
\textbf{MARTA Passenger Traffic} \enspace \textit{(Database Course Project)}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Implemented the UI using \underline{\smash{React.js}} and \underline{\smash{Redux.js}}, and the \underline{REST API} using \underline{\smash{Express.js}} framework and \underline{\smash{MySQL}} database.
\end{itemize}
\vspace{0.5em}
%
\textbf{Declarative DOM} \enspace \textit{UI state dependency/synchronization manager, inspired by frontend Web frameworks (Proof of Concept)}\\
\textbf{Wikipedia Prerequisite Search} \enspace \textit{Breadth-first search of Wikipedia's citation graph (Incomplete)}\\
\textbf{WolframAlpha CLI} \enspace \textit{Command-line utility for solving equations based on \underline{\smash{Wolfram|Alpha XML API}}}\\
\textbf{WebSocket Server}  \enspace \textit{\underline{\smash{Node.js}} implementation of \underline{WebSocket} protocol}\\
\textbf{Todo Apps} \enspace \textit{Implemented using \underline{\smash{React Native}}\underline{\smash{Flutter (Dart)}}, \underline{\smash{SwiftUI}}, \underline{\smash{UIKit (Objective-C)}}, etc. (Proof of Concept)}\\
\textbf{Clean Water Crowdsourcing}	\enspace \textit{Mobile app based on \underline{\smash{Google Maps SDK}} and \underline{\smash{Firebase SDK}} (Android Course Project) }
\vspace{-0.5em}

\section*{TECHNICAL SKILLS}
\textbf{Proficient:} Bash, Vim, Git, JavaScript (ES6), HTML, CSS  \enspace\textbf{Familiar:} C, Java, Swift, Python, MATLAB, shell script, React.js, Redux.js, Angular.js, Vue.js, jQuery, Bootstrap, Node.js, Express.js, Flask, socket.io \enspace\textbf{Used:} Objective-C, C\#, C++, Golang, Kotlin, Dart, TypeScript, SASS/LESS, PHP, SQL, Android, iOS, Xcode, UIKit, SwiftUI, React Native, Flutter, Xamarin, Jupyter Notebook, NumPy, SymPy, Matplotlib, LaTeX

\end{document}
