\documentclass[10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}

\titleformat{\section} {}{\thesection}{1em}{}[{\titlerule[0.3pt]\vspace{-0.4em}}]

\pagestyle{empty}
\begin{document}
\noindent
\parbox{0.25\textwidth}{\hfill\texttt{github.com/GalMunGral}}
\parbox{0.5\textwidth}{\centerline{\Huge\slshape\bfseries Wenqi He}}
\parbox{0.25\textwidth}{\texttt{hewenqi96@gmail.com\\+1(470)343-5207}}
%
\vspace{-1em}
\section*{EDUCATION}
{\itshape 
{\bfseries B.S. Computer Science, Georgia Institute of Technology} \hfill Aug. 2015 -- Dec. 2019}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
	\item Concentrations: Information Internetworks, Modeling and Simulation, Minor: Physics
	\item  Graduated with Highest Honors (cumulative GPA: 3.97/4.0, major: 4.0/4.0, minor: 3.8/4.0)
\end{itemize}
%
\vspace{-0.5em}
\section*{EXPERIENCE}
{\itshape {\bfseries Software Engineer, Etude (\texttt{etudereader.com}), Atlanta} \hfill Sep. 2019 -- Present}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Implemented multiple features for the \textbf{Electron}-based smart PDF reader, including persistent non-contiguous text highlighting and table of contents parsing, which worked on 85\% of user-uploaded PDF documents without bookmarks.
\item Utilized \textbf{PDF.js} to implement the features; detected and fixed a race condition in the default PDF.js viewer between text layer rendering and background computations that caused highlighting bugs on large documents.
\end{itemize}
\vspace{0.5em}
%
{\itshape {\bfseries Front-end Engineer Intern, PegasusCRM, Atlanta} \hfill Jan. -- May. 2018}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Worked on a new feature of the Laravel application that allows merchants to organize their potential customers into lists.
\item Reimplemented main features of \textbf{jQuery} DataTables plugin in \textbf{Vue.js} to allow for future customizations.
\item Used \textbf{Jira} to manage assigned tickets and \textbf{Confluence} to manage internal documentation.
\end{itemize}
%
\vspace{-0.5em}
\section*{SOFTWARE PROJECTS}
{\itshape {\bfseries Georgia Tech Midterm Course Survey System (Web Application)}  \hfill Aug. -- Nov. 2019}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Developed a full-stack web application for the Office of Academic Effectiveness at Georgia Tech that allows students to take surveys anonymously and lets instructors create/edit/close/delete surveys and view survey results.
\item Used \textbf{MongoDB} to store survey templates and responses and implemented a suite of \textbf{Angular components} to render survey forms dynamically based on the \textbf{JSON}-encoded survey template it receives from the back end.
\item Integrated Georgia Tech Login Service (CAS) and Canvas LMS REST API to determine user type and enrollment status, and used \textbf{Angular services} with \textbf{Web Storage} to manage user login status and data requests.
\item Used \textbf{Express/Node.js}, Puppeteer, ldapjs, Salesforce Lightning Design System and \textbf{D3.js}.
\end{itemize}
\vspace{0.5em}
%
{\itshape {\bfseries Public Transport Management System (Web Application, Course Project)} \hfill Sep. -- Nov. 2018}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Developed a full-stack web application that lets MARTA passengers manage personal accounts, transactions and travel histories and lets administrators update station information and review overall traffic and revenues in a time period.
\item Utilized \textbf{MySQL}, \textbf{Express/Node.js}, Sequelize and \textbf{JWT} to build a REST API for the above functionalities.
\item Created two implementations of the front end using \textbf{React/Redux/React Router} and \textbf{Vue/Vuex/Vue Router}. 
\item Deployed the application and database on \textbf{Heroku} and ClearDB.
\end{itemize}
\vspace{0.5em}
%
{\itshape {\bfseries Online Python Console for Chats and Video Interviews (Web Application)}  \hfill May. 2018 -- Aug. 2019}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Developed a web-based \textbf{Python} console that supports dynamic creation of public chat rooms and video interview channels, each with a dedicated REPL instance that runs user-submitted Python code.
\item Used \textbf{Socket.IO} with \textbf{Node.js} to broadcast one user’s messages to other users on the same channel, as well as providing the signaling service that enables the \textbf{WebRTC} video call feature.
\end{itemize}
\vspace{0.5em}
%
{\itshape {\bfseries Server Port Multiplexer/Demultiplexer}  \hfill Jul. 2019}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Developed a system that allows multiple web servers running on the same host to be accessed from a single port by translating between TCP port numbers and URL path prefixes using \textbf{service workers} and a \textbf{Node.js} proxy.
\end{itemize}
\vspace{0.2em}
%
{\itshape {\bfseries Mini Visual Studio Code (Electron Application)}  \hfill May. 2019}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Built a basic desktop file explorer and text editor with \textbf{Electron}, \textbf{React} and \textbf{styled-components}.
\end{itemize}
\vspace{0.2em}
%
{\itshape {\bfseries A Small JavaScript/HTML Parser} \hfill Mar. 2020}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Implemented a shift-reduce parser in JavaScript for a small subset of JavaScript and HTML.
\end{itemize}
\vspace{0.2em}
%
{\itshape {\bfseries JavaScript S-expression Evaluator} \hfill Nov. 2019}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Implemented s-expression, \texttt{eval} and a macro system in JavaScript based on McCarthy's original paper on LISP.
\end{itemize}
\vspace{0.2em}
%
{\itshape {\bfseries Sitting Time Recorder (Mobile Application)}  \hfill Jan. 2019}
\begin{itemize}[leftmargin=15pt, noitemsep, topsep=0pt]
\item Utilized \textbf{iOS} Core Motion and \textbf{Android} sensor framework to detect vertical movements (standing up/sitting down).
\item Used \textbf{Go} with \textbf{MySQL} to record user's daily sitting time and used \textbf{D3.js} with \textbf{SVG} to create calendar heatmaps.
\end{itemize}
%
\vspace{-0.5em}
\section*{TECHNICAL SKILLS}
\textbf{Proficient:} Python, JavaScript/TypeScript, CSS/SCSS, HTML, Bash, Git, Vim\\
\textbf{Familiar:} C, Java, Node.js, Express, React, Angular, Vue.js, jQuery, RxJS, Redux, MySQL/SQL, MongoDB\\
\textbf{Used:} iOS (Objective-C, Swift), Android (Kotlin), Xamarin (C\#), Flutter (Dart), Go/Golang, PHP
\end{document}
